\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-13 paper/draft.tex
[Minor] corrections
Add times for koa

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Applying \sys to three large applications}.
		\fixme{Highlight some things}
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} lll}
\toprule
                    & Koa    & Moeda   &  Terminalizer \\
\midrule
 Size (KB)          & 41M    &  29M    &   262M        \\
 LoC                & 127K   &  79K    &   39K         \\
 Top-level modules  &  24    &  7      &    33         \\
 Total Modules      &  432   &  260    &    1084       \\
 Lya detects:       &  1507  &   729   &     2355      \\
 Baseline           &  xx    &  1.27   &    0.754      \\
 A1 (TF)            &        &  2.00   &    3.346      \\
 A3 (HF)            &        &  2.684  &    2.684      \\
 A8 (Types)         &        &  2.036  &    2.615      \\     
\bottomrule
\end{tabular*}
\label{tab:macro}
\vspace{-5mm}
\end{table}

>>>>

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Applying \sys to three large applications}.
		\fixme{Highlight some things}
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} lll}
\toprule
                    & Koa    & Moeda   &  Terminalizer \\
\midrule
 Size (KB)          & 41M    &  29M    &   262M        \\
 LoC                & 127K   &  79K    &   39K         \\
 Top-level modules  &  24    &  7      &    33         \\
 Total Modules      &  432   &  260    &    1084       \\
 Lya detects:       &  1507  &   729   &     2355      \\
 Baseline           &  0.97  &  1.27   &    0.754      \\
 A1 (TF)            &  1.48  &  2.00   &    3.346      \\
 A3 (HF)            &  1.30  &  2.684  &    2.684      \\
 A8 (Types)         &  1.32  &  2.036  &    2.615      \\     
\bottomrule
\end{tabular*}
\label{tab:macro}
\vspace{-5mm}
\end{table}
